<span style='line-height:60px; font-size:80px'>Catching competitors</span><font size=12>:</font><br><font size=8><span style='line-height:60px'>lexical evolution in diachronic corpora</span></font>

### 2019-07-22 news.Rmd
stirling
cl2019 talk

>>>>

- Presenting a talk on lexical competition at the [CL2019](http://www.cl2019.org/). Slides with interactive plots [here](https://andreskarjus.github.io/cl2019talk.html). Also teaching a dataviz [workshop](https://andreskarjus.github.io/artofthefigure/cl2019).

- Presenting an updated version of the communivative need & lexical competition poster at the [Culture Conference 2019](https://culture-conference.com/programme-2019/) in Stirling, 1-2 July 2019. Online version with interactive plots [here](https://andreskarjus.github.io/lexcom_poster). More languages this time!
